Are We Reusing Outdated and License-Violating \newline Code Snippets from Stack Overflow?

### 2017-02-05 cloneoverflow-latex/cloneoverflow.tex
Updated the numbers.
Updated the classification patterns according to Jens suggestions.

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Cand.} \\ \cline{3-6}
		& \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 181 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 310,803 & & & & & 32,039 \\ 
		\hline
		\multicolumn{7}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 85\%$,}} \\
		\multicolumn{7}{l}{\scriptsize{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}} \\
	\end{tabular} %
%}
\end{table}

\begin{table}
	\centering
	\caption{The online clone classification results}
	\label{tab:online_clone_classification_results}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c|}{Classification} & \multirow{2}{*}{TP} \\ \cline{3-4}
		& & Auto & Manual & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & 9 & 2,299 & x \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,495 & 254 & x \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 17,801 & 16,930 & 871 & 704 \\
		\multirow{1}{*}{$N_D$} & 181 & 10 & 171 & x \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 32,039 & 28,444 & 3,595 & x \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

@@

As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size, regular expressions, and gook/ok pairs. The combination of the three filters reduce the number of $S_D$ clones to 17,801 pairs for manual investigation. 
For $N_D$, 10-line threshold is already a minimum NiCad's clone size. However, NiCad still reported much more clone pairs than Simian since it can detect type-3 clones. Thus, besides regular expressions and good/ok pair filters, we filtered NiCad's clones further by a stricter similarity threshold. We increase NiCad's similarity threshold from 70\% to 85\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.15). We have tried varying the UPI from 70\% (default), 80\%, 85\% and 90\% and we found that 85\% similarity provides the best balance in terms of the amount of reported clones and feasibility for manual investigation. Using the three filters, we reduced the size of $N_D$ clones to 181 pairs.

In our clone classification process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 28,444 pairs out of 32,039 (more than half of the \texttt{equals()} pairs came from \textit{ok} and $S_D$ pairs). Finally, there are 3,595 pairs remaining which we manually classified them. The classification summary is shown in \Cref{tab:online_clone_classification_results}.

\textbf{To answer RQ1, we found 32,039 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets. They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 181 $N_D$ pairs. After classification, we found at least \FIXME{NUMBER} online code clones pairs between Stack Overflow and Qualitas.}

@@

\begin{table}
	\centering
	\caption{Seven patterns of online code cloning}
	\label{tab:classification_scheme}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{c|p{8.4cm}}
			\hline 
			Patt. & Descriptions \\ 
			\hline 
			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
			\hline 
			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
			\hline 
			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
			\\ 
			\hline 
			ES & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
			\\ 
			\hline 
			BP & Boiler-plate or IDE auto-generated
			\\ 
			\hline 
			IN & Inheritance, interface implementation 
			\\ 
			\hline 
			FC & Accidental similarity, false clones \\ 
			\hline 
		\end{tabular}  %
	}
\end{table}

@@

Nevertheless, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as pattern BP. We then added 6 new patterns observed as common cloning patterns from our preliminary study. The seven patterns include QS, SQ, UN, ES, BP, IN, and FC as presented in \Cref{tab:classification_scheme}. QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation/links in Stack Overflow post). Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is the opposite of QS. UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones but without any attribution of copying. They are unique enough not be boiler-plate and inheritance or interface implementation. ES (\textbf{E}xternal \textbf{S}ources) is a cloning that has an evidence of copying from an external source(s). Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of \verb|equals()| methods, getters and setters, or IDE-generated code (e.g.~GUI components). Pattern IN (\textbf{In}heritance/Interface) is cloning because of inheritance of the same super class or implementation of the same interface. They usually share similar overriding methods. The last pattern, FC (\textbf{F}alse \textbf{C}lones), represents false clone pairs. They can be either accidentally similar clones (e.g.~similar \texttt{try-catch} statements), similar clones after code normalisation, or just false positives of the tools. Using the classification patterns, we can also calculate the number of true and false positives. We are looking for unique and meaningful clones in this study. Thus, we consider clone pairs classified into pattern QS, SQ, and UN as true positive, and BP, IN, and FC as false positive.

@@

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & A & A' & B & C & D  & E & F & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 1 & 0 & 4  & 3 & 58  & 6 & 2,189 & 2,261 \\
			\multirow{1}{*}{\textit{ok}}  & 8 & 0 & 29  & 10 & 9,158 & 35 & 82 & 9,322 \\
			\multirow{1}{*}{$S_D$} & 79 & 0 & 336 & 17 & 209 & 63 & 167 & 871 \\
			\multirow{1}{*}{$N_D$} & 8  & 0 & 27 & 1 & 77 & 3 & 82 & 168 \\ 
			\hline
			Total & 96 & 0 & 396 & 31 & 9,502 & 107 & 2,520 & 12,622 \\ 
			\hline
		\end{tabular} 
	}
\end{table}

>>>>

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Cand.} \\ \cline{3-6}
		& \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 88 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 310,803 & & & & & 31,946 \\ 
		\hline
		\multicolumn{7}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 85\%$,}} \\
		\multicolumn{7}{l}{\scriptsize{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}} \\
	\end{tabular} %
%}
\end{table}

\begin{table}
	\centering
	\caption{The online clone classification results}
	\label{tab:online_clone_classification_results}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c|}{Classification} & \multirow{2}{*}{TP} \\ \cline{3-4}
		& & Auto & Manual & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 & 18 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 & 77 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 17,801 & 16,930 & 871 & 525 \\
		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 & 50 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 31,946 & 28,444 & 3,502 & 670 \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

@@

As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size, regular expressions, and gook/ok pairs. The combination of the three filters reduce the number of $S_D$ clones to 17,801 pairs for manual investigation. 
For $N_D$, 10-line threshold is already a minimum NiCad's clone size. However, NiCad still reported much more clone pairs than Simian since it can detect type-3 clones. Thus, besides regular expressions and good/ok pair filters, we filtered NiCad's clones further by a stricter similarity threshold. We increase NiCad's similarity threshold from 70\% to 85\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.15). We have tried varying the UPI from 70\% (default), 80\%, 85\% and 90\% and we found that 85\% similarity provides the best balance in terms of the amount of reported clones and feasibility for manual investigation. Using the three filters, we reduced the size of $N_D$ clones to 88 pairs.

In our clone classification process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the \texttt{equals()} pairs came from \textit{ok} and $S_D$ pairs). Finally, there are 3,502 pairs remaining which we manually classified them. The classification summary is shown in \Cref{tab:online_clone_classification_results}.

\textbf{To answer RQ1, we found 31,946 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets. They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 88 $N_D$ pairs. After classification, we found at least \FIXME{NUMBER} online code clones pairs between Stack Overflow and Qualitas.}

@@

\begin{table}
	\centering
	\caption{Seven patterns of online code cloning}
	\label{tab:classification_scheme}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{c|p{8.4cm}}
			\hline 
			Patt. & Descriptions \\ 
			\hline 
			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
			\hline 
			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
			\hline 
			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
			\\ 
			\hline 
			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
			\\ 
			\hline 
			BP & Boiler-plate or IDE auto-generated
			\\ 
			\hline 
			IN & Inheritance, interface implementation 
			\\ 
			\hline 
			AC & Accidental similarity, false clones \\ 
			\hline 
		\end{tabular}  %
	}
\end{table}

@@

Nevertheless, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as pattern BP. We then added 6 new patterns observed as common cloning patterns from our preliminary study. The seven patterns include QS, SQ, UN, ES, BP, IN, and FC as presented in \Cref{tab:classification_scheme}. QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation/links in Stack Overflow post). Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is the opposite of QS. UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones but without any attribution of copying. They are unique enough not be boiler-plate and inheritance or interface implementation. ES (\textbf{Ex}ternal Sources) is a cloning that has an evidence of copying from an external source(s). Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of \verb|equals()| methods, getters and setters, or IDE-generated code (e.g.~GUI components). Pattern IN (\textbf{In}heritance/Interface) is cloning because of inheritance of the same super class or implementation of the same interface. They usually share similar overriding methods. The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents false clone pairs. They can be either accidentally similar clones (e.g.~similar \texttt{try-catch} statements), similar clones after code normalisation, or just false positives of the tools. Using the classification patterns, we can also calculate the number of true and false positives. We are looking for unique and meaningful clones in this study. Thus, we consider clone pairs classified into pattern QS, SQ, UD, and EX as true positive, and BP, IN, and AC as false positive.

@@

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & QS & SQ & UD & EX & BP  & EX & AC & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 1 & 0 & 4  & 3 & 58  & 6 & 2,189 & 2,261 \\
			\multirow{1}{*}{\textit{ok}}  & 8 & 0 & 29  & 10 & 9,158 & 35 & 82 & 9,322 \\
			\multirow{1}{*}{$S_D$} & 79 & 0 & 336 & 17 & 209 & 63 & 167 & 871 \\
			\multirow{1}{*}{$N_D$} & 8  & 0 & 27 & 1 & 77 & 3 & 82 & 168 \\ 
			\hline
			Total & 96 & 0 & 396 & 31 & 9,502 & 107 & 2,520 & 12,622 \\ 
			\hline
		\end{tabular} 
	}
\end{table}
